Building a continuous benchmarking ecosystem in bioinformatics

### 2024-10-23 manifesto-main.tex
Updates from Overleaf

% Useful packages
\usepackage{amssymb}
\usepackage{siunitx}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
\usepackage{cleveref}
\usepackage[utf8]{inputenc}
\usepackage[right]{lineno}
\usepackage{csquotes}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{adjustbox}
\usepackage{array}
\usepackage{url}
\usepackage{titlesec}
%\usepackage[compatibility=false]{caption}
\usepackage{authblk}
\usepackage{xcolor} % Load the xcolor package for color options
\usepackage{microtype}
%\usepackage{url}
\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref}

@@

\renewcommand{\thetable}{\Roman{table}}

% Define a new format for \subsection
\titleformat{\subsection}
  {\mdseries\itshape\large} % Medium series, italic shape, and large font size
  {\thesubsection}{1em}{} % Numbering, spacing, and the section title itself

@@

\section*{What is a benchmarking system?}
%\label{sec:main_section}

@@

Can benchmarking be systematized? Benchmarks should be orchestrated and run by `benchmarking system's to create `artifacts' (code snapshots, file outputs to be shared, performance outputs).  The various elements of code, especially the details on how datasets are preprocessed and how methods are run, should be explicitly available for scrutiny. Such a system should facilitate components to be public, open and allow contributions (e.g. corrections or new components), such that the benchmarks of the future can run more continuously. At the outset of a benchmark, a benchmark `definition' could be envisioned, which could give a formal specification of the entire set of components (and the pattern of artifacts to be generated). The benchmark definition could even be expressed as a single configuration file that specifies the scope and topology of components to include, details of the repositories (code implementations with versions), the instructions to create software environments (accessible across compute architectures), and the parameters used. A benchmark definition in terms of layers and their corresponding challenges and opportunities within each layer is illustrated in Figure~\ref{fig:layers}.

@@

\pagebreak
\linespread{1.1} 
%\printbibliography

>>>>

% Useful packages
\usepackage{amssymb}
\usepackage{siunitx}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
\usepackage{cleveref}
\usepackage[utf8]{inputenc}
%\usepackage[right]{lineno}
\usepackage{csquotes}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{adjustbox}
\usepackage{array}
\usepackage{url}
\usepackage{titlesec}
%\usepackage[compatibility=false]{caption}
\usepackage{authblk}
\usepackage{xcolor} % Load the xcolor package for color options
\usepackage{microtype}
%\usepackage{url}
\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref}

@@

%\renewcommand{\thetable}{\Roman{table}}

@@

\section*{Why benchmarking systems?}
%\label{sec:main_section}

@@

Can benchmarking be systematized? Benchmarks should be orchestrated and run by \emph{benchmarking systems} to create `artifacts' (code snapshots, file outputs to be shared, performance outputs).  The various elements of code, especially the details on how datasets are preprocessed and how methods are run, should be explicitly available for scrutiny. Such a system should facilitate components to be public, open and allow contributions (e.g. corrections or new components), such that the benchmarks of the future can run more continuously. At the outset of a benchmark, a benchmark `definition' could be envisioned, which could give a formal specification of the entire set of components (and the pattern of artifacts to be generated). The benchmark definition could even be expressed as a single configuration file that specifies the scope and topology of components to include, details of the repositories (code implementations with versions), the instructions to create software environments (accessible across compute architectures), and the parameters used. A benchmark definition in terms of layers and their corresponding challenges and opportunities within each layer is illustrated in Figure~\ref{fig:layers}.

@@

\pagebreak
\linespread{1} 
%\printbibliography
